\documentclass{sig-alternate}


\usepackage{enumitem}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{amstext}
\usepackage{amstext}
\usepackage{pdfpages}
\usepackage{alltt}
\usepackage{epstopdf}
\usepackage{xspace,colortbl}
\usepackage[USenglish]{babel}
\usepackage{multirow}
\usepackage{url}
\usepackage{subfigure}
\usepackage{graphicx}%%
\usepackage{amssymb}
\usepackage{fmtcount}
\usepackage{amsfonts}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
%\usepackage{psfrag}
\usepackage{colortbl}
\usepackage{bm}
\usepackage{times}
\usepackage[nospace]{cite}

\lstset{basicstyle=\tiny,breaklines=true,language=SQL,belowcaptionskip=.25\baselineskip}

\linespread{0.97}

\makeatletter
\def\@copyrightspace{\relax}
\makeatother

\begin{document}

\setlength{\belowdisplayskip}{1pt} \setlength{\belowdisplayshortskip}{1pt}
\setlength{\abovedisplayskip}{1pt} \setlength{\abovedisplayshortskip}{1pt}
\setlength{\belowcaptionskip}{-10pt}
\selectfont

\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\newcommand{\cond}{\textrm{Cond}\xspace}
\newcommand{\dataset}{data set\xspace}
\newcommand{\datasets}{data sets\xspace}
\newcommand{\spview}{\textsf{SPView}\xspace}
\newcommand{\fjview}{\textsf{FJView}\xspace}
\newcommand{\aggview}{\textsf{AggView}\xspace}
\newcommand{\hashfunc}[1]{\textsf{hash}(#1)\xspace}
\newcommand{\hashop}{\textsf{hash}\xspace}
\newcommand{\nsc}{\textsf{NormalizedSC}\xspace}
\newcommand{\rsc}{\textsf{RawSC}\xspace}

\newcommand{\avgfunc}{\ensuremath{\texttt{avg} }\xspace}
\newcommand{\maxfunc}{\ensuremath{\texttt{max} }\xspace}
\newcommand{\minfunc}{\ensuremath{\texttt{min} }\xspace}
\newcommand{\histfunc}{\ensuremath{\texttt{histogram\_numeric} }\xspace}
\newcommand{\countfunc}{\ensuremath{\texttt{count}}\xspace}
\newcommand{\sumfunc}{\ensuremath{\texttt{sum} }\xspace}
\newcommand{\varfunc}{\ensuremath{\texttt{var} }\xspace}
\newcommand{\covfunc}{\ensuremath{\texttt{cov} }\xspace}
\newcommand{\corrfunc}{\ensuremath{\texttt{corr} }\xspace}
\newcommand{\medfunc}{\ensuremath{\texttt{median} }\xspace}
\newcommand{\percfunc}{\ensuremath{\texttt{percentile} }\xspace}
\newcommand{\havingfunc}{\ensuremath{\texttt{HAVING} }\xspace}
\newcommand{\selectfunc}{\ensuremath{\texttt{select} }\xspace}
\newcommand{\ratio}{\ensuremath{\rho }\xspace}


\newcommand{\insertion}{\ensuremath{\texttt{INSERT} }\xspace}
\newcommand{\update}{\ensuremath{\texttt{UPDATE} }\xspace}
\newcommand{\delete}{\ensuremath{\texttt{DELETE} }\xspace}


\newcommand{\tbl}[1]{\textsf{#1}\xspace}
\newcommand{\field}[1]{\textsf{#1}\xspace}
\newcommand{\cost}{\textrm{cost}\xspace}
\newcommand{\ans}{\textsf{ans}\xspace}
\newcommand{\dans}{\Delta\textsf{ans}\xspace}
\newcommand{\cqp}{correction query processing\xspace}
\newcommand{\Cqp}{Correction query processing\xspace}

\newcommand{\reminder}[1]{{{\textcolor{magenta}{\{\{\bf #1\}\}}}\xspace}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\def\ojoin{\setbox0=\hbox{$\bowtie$}%
  \rule[-.02ex]{.25em}{.4pt}\llap{\rule[\ht0]{.25em}{.4pt}}}
\def\leftouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie}}
\def\rightouterjoin{\mathbin{\bowtie\mkern-5.8mu\ojoin}}
\def\fullouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie\mkern-5.8mu\ojoin}}

%\setlength{\belowcaptionskip}{-10pt}

%\newcommand{\reminder}[1] {}
\pagestyle{plain}

\title{Sample-View-Clean: A Data Cleaning Approach for \\Fresh Query Answers From Stale Materialized Views}

\maketitle
\iffalse

\begin{abstract}
Materialized views, stored pre-computed query results, are used to facilitate queries on large datasets.
Materialized views can become out-date when base tables change and queries will give \emph{stale} results.
Maintaining materialized views has been well studied but is often very costly.
In this work, we model the view maintenance problem as a data cleaning problem and treat out-of-date rows materialized views as a type of data error.
In particular, we analyze the maintenance procedure for the views and infer how these updates affect a queries on a the stale view.
For common aggregate queries (\sumfunc, \countfunc, and \avgfunc), we can derive a correction factor from the sample to ``clean" the stale query result.
We bound our corrections in analytic confidence intervals, and in fact, we show that our technique is optimal with respect to estimate variance.
As sampling can be sensitive to long-tailed distributions, we further consider an outlier indexing technique to give increased accuracy when the data distributions are skewed.
We evaluate this approach on real and synthetic datasets and in both a single node (MySQL) and distributed environment (Apache Spark).
In one large scale experiment using 20-node Apache Spark cluster, we derived a 700,000,000 row view from a 1TB activity log base dataset.
We found that maintaining a 5\% sample was 16.3x faster than full maintenance yet only with mean query error of 1.2\%.
\end{abstract}
\fi

\vspace{-1em}

\begin{abstract}
Materialized views (MVs), stored pre-computed query results, are widely used to facilitate fast queries on large datasets. 
%In the Big Data era when new data arrives at an increasingly fast rate, maintaining materialized views can be costly.
%Due to this cost, maintenance is often deferred to a later time, but at the new cost of returning inaccurate query results on stale views.
We address the problem of stale MVs from a data cleaning perspective.
We take inspiration from recent data cleaning results that greatly improve query accuracy by cleaning only a small sample of dirty data.
To complement existing deferred maintenance approaches, we maintain a sample of a materialized view to correct stale query results between maintenance periods, without the cost of full maintenance. 
%This requires an analysis of the view maintenace procedure to efficiently maintain only a sample of a view.
We use this sample to estimate how the updates affect a query on the view, and correct the query results based on this estimate.
We show any query that has an unbiased sample estimator can be reformulated to give an unbiased correction, and for the most common aggregate queries (SUM,COUNT, AVG) our corrections are optimal with respect to estimate variance. 
As sampling can be sensitive to long-tailed distributions, we further explore an outlier indexing technique to give increased accuracy when the data distributions are skewed. 
We evaluate our method on real and synthetic datasets and results suggest that we are able to provide more accurate query results without having to maintain the full view. 
\end{abstract}


\input{introduction.tex}
\input{problem_statement.tex}
\input{architecture.tex}
\input{correction.tex}
%\input{delta.tex}
\input{sampling.tex}
%\input{correction2.tex}
\input{outlier.tex}
%\input{analysis.tex}
\input{experiments.tex}
\input{conclusion.tex}

\bibliographystyle{abbrv}
%\scriptsize
\fontsize{6.00pt}{6.3pt} \selectfont
\bibliographystyle{abbrv}
\bibliography{ref} 

%\input{appendix.tex}

\end{document}